Your Paper Title

### 2025-03-29 paper/paper.qmd
minor citation change

    To begin with, Acevedo's thesis, "Sakura Storytellers" provides a rich cultural context for understanding cherry blossom phenology in Kyoto [@Acevedo2023]. Her research highlights the 1200-year flowering record of Prunus jamasakura in Kyoto, describing it as "the longest and most complete phenological record in existence." These records, compiled from imperial court documents, poetry, and newspaper accounts of hanami celebrations, reveal that Kyoto's cherry trees have responded to major climate fluctuations throughout history, with progressive advancement in bloom dates occurring after approximately 1830. According to Aono and Kazui's analysis referenced in the thesis, cherry trees in Kyoto are currently experiencing warmer conditions than at any time in the past twelve centuries, resulting in average flowering dates that are seven days earlier in the 1971-2000 period compared to historical averages [@Aono2008]. Beyond scientific significance, Acevedo explores how sakura in Kyoto have traditionally served as indicators of agricultural prosperity, with early-falling petals considered inauspicious for rice harvests, demonstrating their enduring role as both cultural and climatic storytellers in Japanese society.

>>>>

    To begin with, Acevedo's thesis, "Sakura Storytellers" provides a rich cultural context for understanding cherry blossom phenology in Kyoto [@Acevedo2021]. Her research highlights the 1200-year flowering record of Prunus jamasakura in Kyoto, describing it as "the longest and most complete phenological record in existence." These records, compiled from imperial court documents, poetry, and newspaper accounts of hanami celebrations, reveal that Kyoto's cherry trees have responded to major climate fluctuations throughout history, with progressive advancement in bloom dates occurring after approximately 1830. According to Aono and Kazui's analysis referenced in the thesis, cherry trees in Kyoto are currently experiencing warmer conditions than at any time in the past twelve centuries, resulting in average flowering dates that are seven days earlier in the 1971-2000 period compared to historical averages [@Aono2008]. Beyond scientific significance, Acevedo explores how sakura in Kyoto have traditionally served as indicators of agricultural prosperity, with early-falling petals considered inauspicious for rice harvests, demonstrating their enduring role as both cultural and climatic storytellers in Japanese society.
